iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-03 manuscript/main.tex
added my other affiliation, plus funding info

\title[iSEE]{iSEE: Interactive SummarizedExperiment Explorer}
\author[Rue-Albrecht \textit{et~al}.]{Kevin Rue-Albrecht\,$^{\text{\sfb 1}}$,
    Federico Marini\,$^{\text{\sfb 2}}$,
    Charlotte Soneson\,$^{\text{\sfb 3}}$
    and Aaron T. L. Lun\,$^{\text{\sfb 4,}*}$} 
\address{$^{\text{\sf 1}}$Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom, \\
$^{\text{\sf 2}}$Institute for Medical Biostatistics, Epidemiology and Informatics, \\
$^{\text{\sf 3}}$University of Zurich and SIB Swiss Institute of Bioinformatics, and \\
$^{\text{\sf 4}}$Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}

@@

\section*{Funding}
ATLL was supported by core funding from Cancer Research UK (award no. 17197 to Dr.\ John Marioni).
\vspace*{-12pt}

>>>>

\title[iSEE]{iSEE: Interactive SummarizedExperiment Explorer}
\author[Rue-Albrecht \textit{et~al}.]{Kevin Rue-Albrecht\,$^{\text{\sfb 1}}$,
    Federico Marini\,$^{\text{\sfb 2}}$,$^{\text{\sfb 3}}$,
    Charlotte Soneson\,$^{\text{\sfb 4}}$
    and Aaron T. L. Lun\,$^{\text{\sfb 5,}*}$} 
\address{$^{\text{\sf 1}}$Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom, \\
$^{\text{\sf 2}}$Center for Thrombosis and Hemostasis (CTH), Mainz, \\
$^{\text{\sf 3}}$Institute for Medical Biostatistics, Epidemiology and Informatics, Mainz, \\
$^{\text{\sf 4}}$University of Zurich and SIB Swiss Institute of Bioinformatics, and \\
$^{\text{\sf 5}}$Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom}

@@

\section*{Funding}
ATLL was supported by core funding from Cancer Research UK (award no. 17197 to Dr.\ John Marioni).
The work of FM is supported by the German Federal Ministry of Education and Research (BMBF 01EO1003).
\vspace*{-12pt}
